---
title: "case-01-ec-rmd"
author: "Angela Wang"
date: "February 26, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
library(MKinfer)
library(survival)
library(survminer)
```

```{r}
data <- read_csv("data/dig.csv")

dig <- data %>%
  filter(TRTMT == 1)

plac <- data %>%
  filter(TRTMT == 0)
```

# Table 1 Values for Digoxin

mean and sd of age
```{r}
round(mean(dig$AGE),1)
round(sd(dig$AGE),1)
```

mean and sd of ejection fraction
```{r}
round(mean(dig$EJF_PER),1)
round(sd(dig$EJF_PER),1)
```

median duration of CHF
```{r}
dig %>%
  filter(!is.na(CHFDUR)) %>%
  summarise(med = median(CHFDUR))
```

prop female
```{r}
dig %>%
  mutate(SEX = case_when(
    SEX == 1 ~ "Male",
    TRUE ~ "Female"
  )) %>%
  count(SEX) %>%
  mutate(freq = round(n / nrow(dig),3)) %>%
  filter(SEX =="Female") 
```

prop non-white
```{r}
dig %>%
  mutate(RACE = case_when(
    RACE == 1 ~ "White",
    TRUE ~ "Non-white"
  )) %>%
  count(RACE) %>%
  mutate(freq = round(n / nrow(dig),3)) %>%
  filter(RACE =="Non-white")
```

prop older than 70
```{r}
dig %>%
  filter(`AGE` > 70) %>%
  count(`AGE` > 70) %>%
  summarise(freq = round(n/nrow(dig),3)) 
```

prop each method of assessing ejection fraction
```{r}
dig %>%
  mutate(`EJFMETH` = case_when(
    `EJFMETH` == 1 ~ "Radionuclide ventriculography",
     `EJFMETH` == 2 ~ "Contrast angiography",
     `EJFMETH` == 3 ~ "Two-dimensional echocardiography")) %>%
  count(`EJFMETH`) %>%
  group_by(`EJFMETH`) %>%
  summarise(freq = round(n / nrow(dig),3))
```
  
prop cardiothoracic ratio
```{r}
dig %>%
  filter(`CHESTX` > .55) %>%
  count(`CHESTX` > .55) %>%
  summarise(freq = round(n/nrow(dig),3)) 
```

prop NYHA class
```{r}
dig %>%
  mutate(`FUNCTCLS` = case_when(
    `FUNCTCLS` == 1 ~"I",
    `FUNCTCLS` == 2 ~"II",
    `FUNCTCLS` == 3 ~"III",
    `FUNCTCLS` == 4~"IV")) %>%
  count(`FUNCTCLS`) %>%
  group_by(`FUNCTCLS`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  drop_na()
```

prop for each number of signs/symptoms
```{r}
dig %>% 
  count(`NSYM`) %>%
  group_by(`NSYM`) %>%
  summarise(freq = round(n / nrow(dig),3)) 
```

prop previous myo infection
```{r}
dig %>%
  count(`PREVMI`) %>%
  group_by(`PREVMI`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`PREVMI` == 1) 
```

prop angina
```{r}
dig %>%
  count(`ANGINA`) %>%
  group_by(`ANGINA`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`ANGINA` == 1)
```

prop diabetes
```{r}
dig %>%
  count(`DIABETES`) %>%
  group_by(`DIABETES`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`DIABETES` == 1) 
```

prop hypertension
```{r}
dig %>%
  count(`HYPERTEN`) %>%
  group_by(`HYPERTEN`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`HYPERTEN` == 1) 
```

prop previous digoxin use
```{r}
dig %>%
  count(`DIGUSE`) %>%
  group_by(`DIGUSE`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`DIGUSE` == 1) 
```

prop primary cause nonischemic or ischemic
```{r}
dig %>% 
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  count(`CHFETIOL_ni`) %>%
  group_by(`CHFETIOL_ni`) %>%
  summarise(freq = round(n / nrow(dig),3))
```

prop primary cause within nonischemic 
```{r}
dig %>% 
  mutate(`CHFETIOL` = case_when(
    `CHFETIOL` == 3 |`CHFETIOL`== 6 |`CHFETIOL`== 5 ~ "Other",
    `CHFETIOL` == 1 ~ "Ischemic",
    `CHFETIOL` == 2 ~ "Hypertensive",
    `CHFETIOL` == 4 ~ "Idiopathic")) %>%
  count(`CHFETIOL`) %>%
  group_by(`CHFETIOL`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  drop_na() %>%
  filter(CHFETIOL %in% c("Hypertensive", "Idiopathic", "Other"))
```

prop diuretics
```{r}
dig %>% 
  mutate(`diurets` = case_when(
   `DIURET` == 1 | `DIURETK` == 1 ~ "Diuretics")) %>%
  count(`diurets`) %>%
  group_by(`diurets`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(diurets == "Diuretics")
```

prop ace inhibitor
```{r}
dig %>%
  count(`ACEINHIB`) %>%
  group_by(`ACEINHIB`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`ACEINHIB` == 1) 
```

prop nitrates
```{r}
dig %>%
  count(`NITRATES`) %>%
  group_by(`NITRATES`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`NITRATES` == 1) 
```

prop other vasodilators
```{r}
dig %>%
  count(`VASOD`) %>%
  group_by(`VASOD`) %>%
  summarise(freq = round(n / nrow(dig),3)) %>%
  filter(`VASOD` == 1) 
```

prop daily dose 
```{r}
dig %>%
  filter(`DIGDOSE` %in% c(0.125, 0.250, 0.375, 0.500)) %>%
  count(`DIGDOSE`) %>%
  group_by(`DIGDOSE`) %>%
  summarise(freq = round(n / nrow(dig),3))
```


# Table 1 Values for Placebo

mean and sd of age
```{r}
round(mean(plac$AGE),1)
round(sd(plac$AGE),1)
```

mean and sd of ejection fraction
```{r}
round(mean(plac$EJF_PER),1)
round(sd(plac$EJF_PER),1)
```

median duration of CHF
```{r}
plac %>%
  filter(!is.na(CHFDUR)) %>%
  summarise(med = median(CHFDUR))
```

prop female
```{r}
plac %>%
  mutate(SEX = case_when(
    SEX == 1 ~ "Male",
    TRUE ~ "Female"
  )) %>%
  count(SEX) %>%
  mutate(freq = round(n / nrow(plac),3)) %>%
  filter(SEX =="Female") 
```

prop non-white
```{r}
plac %>%
  mutate(RACE = case_when(
    RACE == 1 ~ "White",
    TRUE ~ "Non-white"
  )) %>%
  count(RACE) %>%
  mutate(freq = round(n / nrow(plac),3)) %>%
  filter(RACE =="Non-white")
```

prop older than 70
```{r}
plac %>%
  filter(`AGE` > 70) %>%
  count(`AGE` > 70) %>%
  summarise(freq = round(n/nrow(plac),3)) 
```

prop each method of assessing ejection fraction
```{r}
plac %>%
  mutate(`EJFMETH` = case_when(
    `EJFMETH` == 1 ~ "Radionuclide ventriculography",
     `EJFMETH` == 2 ~ "Contrast angiography",
     `EJFMETH` == 3 ~ "Two-dimensional echocardiography")) %>%
  count(`EJFMETH`) %>%
  group_by(`EJFMETH`) %>%
  summarise(freq = round(n / nrow(plac),3))
```
  
prop cardiothoracic ratio
```{r}
plac %>%
  filter(`CHESTX` > .55) %>%
  count(`CHESTX` > .55) %>%
  summarise(freq = round(n/nrow(plac),3)) 
```

prop NYHA class
```{r}
plac %>%
  mutate(`FUNCTCLS` = case_when(
    `FUNCTCLS` == 1 ~"I",
    `FUNCTCLS` == 2 ~"II",
    `FUNCTCLS` == 3 ~"III",
    `FUNCTCLS` == 4~"IV")) %>%
  count(`FUNCTCLS`) %>%
  group_by(`FUNCTCLS`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  drop_na()
```

prop for each number of signs/symptoms
```{r}
plac %>% 
  count(`NSYM`) %>%
  group_by(`NSYM`) %>%
  summarise(freq = round(n / nrow(plac),3)) 
```

prop previous myo infection
```{r}
plac %>%
  count(`PREVMI`) %>%
  group_by(`PREVMI`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`PREVMI` == 1) 
```

prop angina
```{r}
plac %>%
  count(`ANGINA`) %>%
  group_by(`ANGINA`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`ANGINA` == 1)
```

prop diabetes
```{r}
plac %>%
  count(`DIABETES`) %>%
  group_by(`DIABETES`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`DIABETES` == 1) 
```

prop hypertension
```{r}
plac %>%
  count(`HYPERTEN`) %>%
  group_by(`HYPERTEN`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`HYPERTEN` == 1) 
```

prop previous digoxin use
```{r}
plac %>%
  count(`DIGUSE`) %>%
  group_by(`DIGUSE`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`DIGUSE` == 1) 
```

prop primary cause nonischemic or ischemic
```{r}
plac %>% 
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  count(`CHFETIOL_ni`) %>%
  group_by(`CHFETIOL_ni`) %>%
  summarise(freq = round(n / nrow(plac),3))
```

prop primary cause within nonischemic 
```{r}
plac %>% 
  mutate(`CHFETIOL` = case_when(
    `CHFETIOL` == 3 |`CHFETIOL`== 6 |`CHFETIOL`== 5 ~ "Other",
    `CHFETIOL` == 1 ~ "Ischemic",
    `CHFETIOL` == 2 ~ "Hypertensive",
    `CHFETIOL` == 4 ~ "Idiopathic")) %>%
  count(`CHFETIOL`) %>%
  group_by(`CHFETIOL`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  drop_na() %>%
  filter(CHFETIOL %in% c("Hypertensive", "Idiopathic", "Other"))
```

prop diuretics
```{r}
plac %>% 
  mutate(`diurets` = case_when(
   `DIURET` == 1 | `DIURETK` == 1 ~ "Diuretics")) %>%
  count(`diurets`) %>%
  group_by(`diurets`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(diurets == "Diuretics")
```

prop ace inhibitor
```{r}
plac %>%
  count(`ACEINHIB`) %>%
  group_by(`ACEINHIB`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`ACEINHIB` == 1) 
```

prop nitrates
```{r}
plac %>%
  count(`NITRATES`) %>%
  group_by(`NITRATES`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`NITRATES` == 1) 
```

prop other vasodilators
```{r}
plac %>%
  count(`VASOD`) %>%
  group_by(`VASOD`) %>%
  summarise(freq = round(n / nrow(plac),3)) %>%
  filter(`VASOD` == 1) 
```

prop daily dose 
```{r}
plac %>%
  filter(`DIGDOSE` %in% c(0.125, 0.250, 0.375, 0.500)) %>%
  count(`DIGDOSE`) %>%
  group_by(`DIGDOSE`) %>%
  summarise(freq = round(n / nrow(plac),3))
```

#Table 4 Digoxin Values

ejection fraction .25-.45
```{r}
dig %>%
  filter(`EJF_PER` >= 25 & `EJF_PER` <= 45) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

ejection fraction < .25
```{r}
dig %>%
  filter(`EJF_PER` < 25) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

previous use of digoxin
```{r}
dig %>%
  mutate(`DIGUSE` = case_when(
   `DIGUSE` == 1 ~ "Yes",
   TRUE ~ "No")) %>%
  group_by(DIGUSE) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cause of heart failure
```{r}
dig %>%
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  group_by(CHFETIOL_ni) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cardiothoracic ratio <= .55
```{r}
dig %>%
  filter(`CHESTX` <= .55) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cardiothoracic ratio > .55
```{r}
dig %>%
  filter(`CHESTX` > .55) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

nyha class
```{r}
dig %>%
  mutate(`FUNCTCLS` = case_when(
   `FUNCTCLS` == 1 | `FUNCTCLS` == 2 ~ "1 or 2",
   TRUE ~ "3 or 4")) %>%
  group_by(FUNCTCLS) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

overall study
```{r}
dig %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

#Table 4 Placebo Values 

ejection fraction .25-.45
```{r}
plac %>%
  filter(`EJF_PER` >= 25 & `EJF_PER` <= 45) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

ejection fraction < .25
```{r}
plac %>%
  filter(`EJF_PER` < 25) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

previous use of digoxin
```{r}
plac %>%
  mutate(`DIGUSE` = case_when(
   `DIGUSE` == 1 ~ "Yes",
   TRUE ~ "No")) %>%
  group_by(DIGUSE) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cause of heart failure
```{r}
plac %>%
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  group_by(CHFETIOL_ni) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cardiothoracic ratio <= .55
```{r}
plac %>%
  filter(`CHESTX` <= .55) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

cardiothoracic ratio > .55
```{r}
plac %>%
  filter(`CHESTX` > .55) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

nyha class
```{r}
plac %>%
  mutate(`FUNCTCLS` = case_when(
   `FUNCTCLS` == 1 | `FUNCTCLS` == 2 ~ "1 or 2",
   TRUE ~ "3 or 4")) %>%
  group_by(FUNCTCLS) %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

overall study
```{r}
plac %>%
  count(`DWHF`) %>%
  mutate(freq= round(n/sum(n),3)) %>%
  filter(DWHF == 1)
```

#Table 4: Absolute Difference 

absolute dif ejection fraction .25-.45
```{r}
dif1 = (613/2270) - (735/2273)
result1 = prop.test(x = c(613,735), n=c(2270,2273), conf.level =.95, correct = FALSE)
x1 = result1$conf.int
print(round(dif1,3))
print(round(x1,3))
```

absolute dif ejection fraction <.25
```{r}
dif2 = (428/1127) - (556/1130)
result2 = prop.test(x = c(428,556), n=c(1127,1130), conf.level =.95, correct = FALSE)
x2 = result2$conf.int
print(round(dif2,3))
print(round(x2,3))
```

absolute dif previous digoxin use = yes
```{r}
dif1 = (550/1498) - (688/1519)
result1 = prop.test(x = c(550,688), n=c(1498,1519), conf.level =.95, correct = FALSE)
x1 = result1$conf.int
print(round(dif1,3))
print(round(x1,3))
```

absolute dif previous digoxin use = no
```{r}
dif2 = (491/1899) - (603/1884)
result2 = prop.test(x = c(491,603), n=c(1899,1884), conf.level =.95, correct = FALSE)
x2 = result2$conf.int
print(round(dif2,3))
print(round(x2,3))
```

absolute dif cause of heart failure = ischemic
```{r}
dif1 = (731/2405) - (873/2398)
result1 = prop.test(x = c(731,873), n=c(2405,2389), conf.level =.95, correct = FALSE)
x1 = result1$conf.int
print(round(dif1,3))
print(round(x1,3))
```

absolute dif cause of heart failure = nonischemic
```{r}
dif2 = (306/983) - (413/996)
result2 = prop.test(x = c(306,413), n=c(983,996), conf.level =.95, correct = FALSE)
x2 = result2$conf.int
print(round(dif2,3))
print(round(x2,3))
```

absolute dif ct ratio <= .55
```{r}
dif1 = (600/2220) - (724/2233)
result1 = prop.test(x = c(600,724), n=c(2220,2233), conf.level =.95, correct = FALSE)
x1 = result1$conf.int
print(round(dif1,3))
print(round(x1,3))
```

absolute dif ct ratio > .55
```{r}
dif2 = (441/1176) - (567/1170)
result2 = prop.test(x = c(441,567), n=c(1176,1170), conf.level =.95, correct = FALSE)
x2 = result2$conf.int
print(round(dif2,3))
print(round(x2,3))
```

absolute dif nyha class = 1 or 2
```{r}
dif1 = (601/2275) - (739/2296)
result1 = prop.test(x = c(601,739), n=c(2275,2296), conf.level =.95, correct = FALSE)
x1 = result1$conf.int
print(round(dif1,3))
print(round(x1,3))
```

absolute dif nyha class = 3 or 4
```{r}
dif2 = (438/1118) - (552/1105)
result2 = prop.test(x = c(438,552), n=c(1118,1105), conf.level =.95, correct = FALSE)
x2 = result2$conf.int
print(round(dif2,3))
print(round(x2,3))
```

absolute dif overall pop
```{r}
dif = (1041/3397) - (1291/3403)
result = prop.test(x = c(1041,1291), n=c(3397,3403), conf.level =.95, correct = FALSE)
x = result$conf.int
print(round(dif,3))
print(round(x,3))
```

#Table 4: Risk Ratio

risk ratio ejection fraction .25-.45
```{r}
data2 <- data %>%
  filter(EJF_PER >= 25 & EJF_PER <= 45) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio ejection fraction <.25
```{r}
data2 <- data %>%
  filter(EJF_PER < 25) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio previous digoxin use = yes
```{r}
data2 <- data %>%
  filter(DIGUSE == 1) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio previous digoxin use = no
```{r}
data2 <- data %>%
  filter(DIGUSE == 0) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio cause of heart failure = ischemic
```{r}
data2 <- data %>%
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  filter(CHFETIOL_ni == "Ischemic") 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio cause of heart failure = nonischemic
```{r}
data2 <- data %>%
  mutate(`CHFETIOL_ni` = case_when(
   `CHFETIOL` == 1 ~ "Ischemic",
   TRUE ~ "Nonischemic")) %>%
  filter(CHFETIOL_ni == "Nonischemic") 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio ct ratio <= .55
```{r}
data2 <- data %>%
  filter(CHESTX <= .55) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio ct ratio > .55
```{r}
data2 <- data %>%
  filter(CHESTX > .55) 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```


risk ratio nyha = 1 or 2
```{r}
data2 <- data %>%
  mutate(`FUNCTCLS` = case_when(
   `FUNCTCLS` == 1 | `FUNCTCLS` == 2 ~ "1 or 2",
   TRUE ~ "3 or 4")) %>%
  filter(FUNCTCLS == "1 or 2") 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio nyha = 3 or 4
```{r}
data2 <- data %>%
  mutate(`FUNCTCLS` = case_when(
   `FUNCTCLS` == 1 | `FUNCTCLS` == 2 ~ "1 or 2",
   TRUE ~ "3 or 4")) %>%
  filter(FUNCTCLS == "3 or 4") 
  
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data2)
sum <- summary(coxm1)
sum$conf.int
```

risk ratio overall pop
```{r}
coxm1 <- coxph(Surv(DWHFDAYS, DWHF) ~ TRTMT, data = data)
sum <- summary(coxm1)
sum$conf.int
```


#Discussion
The values I calculated for table 1 and table 4 are mostly exactly correct, but there are a few values that were slightly off from the ones in the report. There are a few more discrepancies in table 1 than in table 4. 

Discrepancies in Table 1:
Digoxin: sd of ejection fraction, percent non white, percent >= 4 signs or symptoms of CHF, percent nonischemic cause of CHF, percent other cause of CHF, percent nitrates

Placebo: percent nonischemic cause of CHF, percent hypertensive cause of CHF, percent idiopathic cause of CHF, percent taking daily dose of .250 mg

Discrepancies in Table 4:
Digoxin:percent nonischemic cause of CHF

Placebo: percent nonischemic cause of CHF, percent in NYHA class 3 or 4

Absolute Difference: cause of heart failure

Most of them only differ by .1% or .2% for the proportions and .01 or .02 in the ratios. These are most likely due to errors in rounding. It seems that calculations involving nonischemic cause of CHF are consistently off by a little bit. This variable was one that the researchers made, and they were not explicitly clear how they did so. Therefore, there could be slight differences in how I coded this variable with how the researchers did.  